\documentclass[10pt,a4]{article}

\usepackage[letterpaper, portrait, margin=1cm]{geometry}	% To set Page Margin
\usepackage{setspace}										% To use vspace
\usepackage{tabu}											% To create personal details table
\usepackage{multirow}										% To merge cells in table
\usepackage{color}											% To change font color
\usepackage{hyphenat}										% To remove hyphenation
\usepackage[hidelinks]{hyperref}							% To insert hyperlink for mail ID
\usepackage{textcomp}										% To display Celsius symbol 
\usepackage{enumitem}										% To create list
\usepackage{tabto}											% To use \tab
\usepackage{gensymb}										% Degree symbol
\usepackage{xcolor}

\renewcommand{\labelitemi}{\textendash}						% Change the bullet type

\def\hrulefill{\leavevmode\leaders\hrule height 1pt\hfill\kern0pt}		% To change default thickness of \hrulefill

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\setlist{nosep}												% To remove space between list items



\begin{document}
{\fontfamily{ptm}\selectfont	
	\renewcommand{\familydefault}{\sfdefault}
	\pagenumbering{gobble}									% To remove page number

% ---------- ---------- ---------- ---------- ---------- ---------- ---------- ---------- ---------- ---------- ---------- ----------
% Personal Details
	\noindent
	\begin{tabu} to \textwidth {X[1] X[c] X[r]}
		  &  \multirow{1}{*}{{\textbf{\Large Narain Pattabhiraman}}}  &   		\\
	\end{tabu}

    % \vspace{-2mm}
    % \begin{center}
    % \begin{tabular} {p{0.25\textwidth} p{0.25\textwidth} p{0.20\textwidth} p{0.24\textwidth}}
    %     \raggedright\href{https://wwww.linkedin.com/in/narainp}{\textcolor{blue}{www.linkedin.com/in/narainp}} & 
    %     \href{https://github.com/narain1}{\textcolor{blue}{github.com/narain1}} & 
    %     \href{https://narain1.netlify.app/}{\textcolor{blue}{narain1.netlify.app}} & 
    %     \raggedright\href{mailto:narain13579@gmail.com}{\textcolor{blue}{narain13579@gmail.com}} 
    % \end{tabular}
    % \end{center}
 
    % \hspace*{50pt}
	
	% \centering	\\

    \begin{center}
    \begin{tabular} {p{0.25\textwidth} p{0.20\textwidth} p{0.20\textwidth} p{0.20\textwidth}}
        \raggedright\href{https://wwww.linkedin.com/in/narainp}{\textcolor{blue}{Linkedin}} & 
        \href{https://github.com/narain1}{\textcolor{blue}{Github}} & 
        \href{https://about.narain.dev}{\textcolor{blue}{Portfolio}} & 
        \raggedright\href{mailto:narain13579@gmail.com}{\textcolor{blue}{narain13579@gmail.com}} 
    \end{tabular}
    \end{center}
    
    \vspace{-2mm}

	
% Education
\vspace{0.25mm}
\begin{flushleft}
	%	\rule{0.5 cm}{1pt}
	{\Large \textbf{EDUCATION}} %\hrulefill	\\
    
    	\hspace{1.5mm} \textbf{\large Arizona State University}, \textit{M.S, Computer Engineering, Computer Systems}  \hfill \textit{Aug '23 $-$ May '25}	\\
        
        \hspace{1.5mm} \textbf{\large Amrita Vishwa Vidyapeetham}, \textit{\ B.Tech., Mechanical Engineering} \hfill \textit{ Jul '16 - Jun '20}	\\

\end{flushleft}

% \vspace{0.5mm}
\begin{flushleft}
		%\rule{0.5cm}{1pt} 
    {\Large \textbf {SKILLS AND CERTIFICATIONS}}
    
        % \vspace{1mm}
            \hspace{0.5cm}  \textbf{Programming Languages:} Python, C/C++, Spark, SQL, CUDA, Triton, LLVM. \\
            \hspace{0.5cm}  \textbf{Machine Learning and Data Science:} MLOps, Computer Vision, NLP, GenAI, LLMs, Airflow, Sagemaker. \\
            \hspace{0.5cm}  \textbf{Cloud Technologies} AWS, Azure, Docker, DevOps, Git, Terraform, Jenkins, Kubernetes, Kafka. \\
            \hspace{0.5cm}  \textbf{Frameworks and Tools:} REST, Websocket, Pytorch, Clang, LLVM, GDB, VLLM, Autogen, Unsloth. \\
            % \hspace{0.5cm}  \textbf{Systems \& Architectures:} Distributed Systems, Embedded systems, GPU. \\
            % \hspace{0.5cm}  \textbf{Relavent Cou:} Embeddings/LLM Alignment, Multimodal Embeddings, 3D Perception.

            % \hspace{0.5cm} \textbf{Relevant Coursework and Certifications:} Embedded Machine Learning, Digital Image Processing, MLSYS, HPC. \\
        
            % \textbf{Soft Skills:} Problem Solving, Critical Thinking, Communication, Teamwork and Leadership

\end{flushleft}
		
    % \vspace{-2mm}
		
% Work Experience
\begin{flushleft}
	%	\rule{0.5cm}{1pt} 
    {\Large \textbf{WORK EXPERIENCE}} %\hrulefill \\

    \vspace{1.5mm}
    \hspace{1.5mm} \textbf{\large AI Engineer (Full-Time), \href{https://ai.asu.edu/ai-tools/ai-acceleration-team}{ASU Enterprise Technology}}, Tempe, USA \hfill \textit{\large May '25 $-$ Present} \\
    \hspace{1.5mm} \textbf{\large MLOps \& AI Development Engineer, \href{https://ai.asu.edu/ai-tools/ai-acceleration-team}{ASU Enterprise Technology}}, Tempe, USA \hfill \textit{\large Jan '24 $-$ May '25}
    \begin{itemize}
        % \item Optimized \textbf{Computer Vision} and \textbf{ASR} models on edge devices, leveraging \textbf{CUDA/Arm Neon} and for real-time processing.
        \item Built a \textbf{dynamic agentic DAG workflow engine} that supports heterogeneous \textbf{LLMs} and \textbf{tools}, allowing on-the-fly composition of complex, multi-step workflows with adaptive routing and tool selection.
        \item \textbf{Built LLM infrastructure} on ASU’s SOL Cluster using Kubernetes, enabling dynamic resource scaling for inference.
        % \item \textbf{Optimized infrastructure} to support a diverse suite of university research models, ensuring high availability and cost-efficiency.
        \item Trained \textbf{Embedding Models} for Domain specific documents using \textbf{MLM Pretraining}, with  \textbf{DeBERTa} architecture.
        % \item Engineered the backend for \textbf{ASUGPT}, an AI assistant using multiple \textbf{LLMs}, supporting students and professors across ASU.
        \item Developed the backend for \textbf{CreateAI}, an \textbf{LLM-powered} chat assistant featuring \textbf{multi-model support}, \textbf{rate monitoring}, \textbf{RAG}, \textbf{agentic evaluation} to prevent hallucinations and \textbf{semantic caching}.

        % \item Implemented \textbf{Vector Databases} and \textbf{Data Pipelines} on \textbf{OpenSearch} for scalable Information retrieval.
        % \item Implemented a \textbf{Teacher-Student model} to propose candidate sequences for the large model to verify, achieving \textbf{2X-3X speedup}.
        \item Engineered a indexing system for \textbf{multimodal question answering}, integrating \textbf{text, video, image} representations for data retrieval.
        \item Implemented \textbf{serverless inference of ML models} on AWS Lambda using \textbf{GGML}, significantly improving scalability and flexibility by enabling deployment of custom models at scale and at reduced cost compared to established model providers.

    \end{itemize}	
    
    \vspace{0.5mm}
    \hspace{1.5mm} \textbf{\large Software Engineer, Fidelity Investments},  Chennai, India \hfill \textit{\large Apr '22 $-$ Jul '23}	\\
    \begin{itemize}
        \item Developed and implemented robust \textbf{Infrastructure and Pipelines} for the deployment of \textbf{Machine Learning Models} on \textbf{AWS}.  
         \item Engineered \textbf{Online Feature Stores} to support real-time data and optimized batch inferencing to handle large-scale data.
         \item Contributed to the development and deployment of diverse machine learning models, including \textbf{Document Layout Models}.
         % \item Crafted and executed deployment pipelines for Low-Latency Models on AWS EC2, utilizing quantized training methods to optimize performance and cost-efficiency. 
         \item Led the deployment and performance optimization of \textbf{Large Language Models}, including \textbf{BLOOM} and \textbf{Flan-T5}, using \textbf{Tensor and Model Parallelism} to accelerate token generation and enhance model performance.
        \item \textbf{Collaborated in deploying scalable machine learning workflows}, ensuring efficient model and data lifecycle management.
    \end{itemize}	
    
    \vspace{0.5mm}
    \hspace{1.5mm} \textbf{\large AI Researcher, QPIAI Technologies},  Bangalore, India \hfill \textit{\large May '21 $-$ Apr '22}	\\
    \begin{itemize}
        \item Implemented a \textbf{Graph Convolutional Network (GCN)} to train graph contrastive learning models for different circuit layouts, achieving high recall in identifying similarities between different circuit layouts.
        \item Introduced a custom \textbf{Ranking Algorithms} for product recommendations supporting automated price estimation for sales.
        \item Involved in developing \textbf{Safety Monitoring Systems} in warehouses using cameras to ensure compliance with social distancing.
        \item \textbf{Developed an AutoML platform for ML models}, enabling automatic hyperparameter tuning and model selection.
        \item Contributed to the hardware/software co-design process focusing on algorithmic optimizations to maximize inferencing throughput.
        
    \end{itemize}		

    \vspace{0.5mm}
    \hspace{1.5mm} \textbf{\large Data Analyst, Thoughtware Analytics},  Bangalore, India \hfill \textit{\large Jan '20 $-$ May '21}	\\		
    \begin{itemize}
          
        \item Conducted \textbf{Demand Forecasting} for manufacturing and service-oriented businesses, focusing on \textbf{Supply Chain Improvements}.
        \item Developed \textbf{Computer Vision} based for quality assurance in manufacturing processes, reducing material waste.  
        \item \textbf{Conducted operational research to optimize logistics}, utilizing advanced algorithms to improve route planning and resource allocation, reducing costs and delivery times.
    \end{itemize}

    \vspace{1.0mm}
    \hspace{1.5mm} \textbf{\large Open Source Contributions}
    \begin{itemize}
        \item \textbf{Pytorch, Pytorch-lightning, Albumentations, Kornia}.
    \end{itemize}
\end{flushleft}




% \begin{flushleft}
%     {\Large \textbf{ACHIEVEMENTS}}
%       % \vspace{1.0mm}
%       \begin{itemize}
%             \item \textbf{Winner, 1st Place} – Hackathon, Amrita University: Developed an innovative solution for real-time drone tracking and planning.
%             \item \textbf{Top Finisher} – TVS Finance: Excelled in predictive modeling for credit scoring among 1000 participants worldwide.
%             % \item \textbf{Large Language Model Inference Optimizations} \hfill \textit{DISML conference 2024}
%       \end{itemize}
\end{flushleft}

\begin{flushleft}
    {\Large \textbf{PROJECTS}}
        \vspace{0.5mm}
        % \item \hspace{1.5mm} \textbf{\large \href{https://huggingface.co/spaces/narainp/Deep-Steganalysis-detector}{{Detection of hidden information from steganographic images}}}
        % \vspace{0.25mm}
        % \begin{itemize}
        %     \item Generated a comprehensive synthetic dataset consisting of images with and without steganographic encoding using three prominent algorithms $-$ JMiPOD, JUNIWARD, and UERD $-$ across various JPEG compression ratios.
        %     \item Developed a \textbf{CNN} based on \textbf{ResNet} with \textbf{Channel Attention} and reduced convolutions stride to enhance detection of subtle steganographic signals in digital images that effectively differentiates between various levels of JPEG compression.
            
        %     \item Engineered a 12-class detection system that effectively differentiates between various levels of JPEG compression and steganography types, significantly boosting the model’s accuracy and sensitivity.
        % \end{itemize}
        % \hspace{1.5mm} 
        

        % \item \hspace{1.5mm} \textbf{\large High-Performance JIT Compilation for Python Using LLVM}
        % \begin{itemize}
        %     \item Developed a \textbf{JIT compilation framework} for Python, leveraging \textbf{LLVM IR} to significantly optimize function execution.
        %     \item Implemented multiple JIT strategies \textbf{AST, Bytecode, Tracing JIT}, transforming Python functions into optimized machine code.
        %     \item Achieved up to \textbf{5000x speed improvements} by dynamically compiling and optimizing performance-critical functions.
        %     \item Integrated \textbf{constant folding} and additional compiler optimizations to enhance runtime efficiency, benchmarking against \textbf{Numba}.
        % \end{itemize}

        % \item \hspace{1.5mm} \textbf{\large Thesis project: Robotic Arm Maneuvering Using Deep Reinforcement Learning (DRL)}
        \item \hspace{1.5mm} \textbf{\large Robotic Arm Maneuvering Using Deep Reinforcement Learning}
        % \vspace{0.2mm} \\
        \hfill \textit{B.Tech Thesis Project, Amrita Vishwa Vidyapeetham}

        \vspace{0.25mm}
        \begin{itemize}
            % \item Designed and implemented a simulation environment for a robotic arm in \textbf{Unity3D}, integrating \textbf{ML-Agents} toolkit for reinforcement learning research.
            \item Designed and implemented a simulation environment for a robotic arm in \textbf{Unity3D} with the \textbf{Pytorch}, and fabricated a physical prototype using \textbf{3D-printed components} and \textbf{servo motors} for real-world experimentation.
            \item Developed and trained agents using advanced RL algorithms: \textbf{DDPG}, \textbf{A2C}, and \textbf{PPO} for sample-efficient on-policy learning.
            \item Engineered continuous control tasks with \textbf{($>$30 DoF)}, leveraging neural network policies to process raw sensor data and image.
            % \item Automated reward, implemented \textbf{experience replay} and \textbf{Ornstein-Uhlenbeck noise} for robust exploration and stable training.
            \item Demonstrated successful transfer of neural network control policies trained in simulation to the real-world robotic arm.
            % \item Achieved target performance benchmarks, enabling the robotic arm to accurately follow moving targets and generalize control policies to novel environments.
        \end{itemize}
        \item \hspace{1.5mm} \textbf{\large Compiler System for Graph Optimization and Op-Fusion for Deep Learning}
        \vspace{0.25mm}
        \begin{itemize}
            \item Engineered a compiler system targeting mobile backends with heterogeneous computer architecture.
            \item Implemented a kernel mapping strategy leveraging \textbf{TVM} and \textbf{TASO}, enhancing performance.
            \item Designed \textbf{high performant SIMD kernels} for \textbf{Edge Devices (ARM NEON)} for \textbf{Computer Vision algorithms}.
            \item Developed \textbf{Custom CUDA kernels} for \textbf{Jetson Orin}, achieving speedups benchmarked against OpenCV C++ for \textbf{ARM Devices}.
        \end{itemize}


\end{flushleft}


}
	
\end{document}
